---
title: 'Homework #3: Matching'
author: Eric Cheng, Julio Guzman, Vinh Luong, Jorge Ortega, Shao Zhu
output: pdf_document
fontsize: 12
geometry: margin=0.6in
---


# Load the data

```{r}
load("HW3df.rdat")
summary(df)
```

# Some Simple plots

Distribution of Women Senders

```{r}
barplot(table(df[df$SenderGender==1,]$SenderLooks))
```

Distribution of Men Senders

```{r}
barplot(table(df[df$SenderGender==2,]$SenderLooks))
```



```{r}
# pred.prob.male=function(Xfemale){
#  predict(lres.m,newdata=data.frame(ReceiverLooks=factor(Xfemale,levels=1:11)),type='response')
# }
```
# And similarly for women
```{r}
# pred.prob.female=function(Xmale){
#  predict(lres.f,newdata=data.frame(ReceiverLooks=factor(Xmale,levels=1:11)),type='response')
#}
```



# Q3: Using the pred.match function explore the match scores between 
#     men and women at various looks percentiles. Comment on and 
#     explain your findings. For example, you may want to explore 
#     why pred.match(2,10) differs from pred.match(10,2).    
    
# Q4: (Optional: Warning Difficult and Time Consuming!) 
#     How would you change the match function to account 
#     for the findings in Q2. How do the results comapre to
#     the original pred.match function results.


